### 2013-01-15 edupar-13/conclusion.tex
Finish conclusion

% some things we can automate -- inspired by automatic malloc instrumentation -- but some things require changing the spec

\subsubsection{Automatic instrumentation}
TODO

\subsubsection{Mandating API names}
For example, rather than providing \x{tell_landslide_thread_runnable()}, we could mandate that the scheduler's code path to making a thread runnable include a function with a specified name.

\subsubsection{Mandating design}
TODO

@@

Landslide needs to be extended to cope with the multiple scheduler queues that occur in multi-core hardware, however, much of this can be managed with slight variations of the annotations student provide, naming the core a thread will runs on, for example.

To fully realize this benefit Landslide usability should be improved.
For example, our class notes communicate execution sequencing with a tabular representation of thread execution; Landslide's presentation of a buggy sequence could be tailored to match our teaching methodology.

% this should all turn into a bulleted list of improvement areas
Tool usability is greatly improved by lowering the start up effort required of each student.
Much of the annotation our students must add to their kernel could be eliminated if the course project specification required prescribed names for prescribed functions, so Landslide could easily identify what the student kernel is doing.
There is a downside to doing too much of this, as the design of kernel interfaces is an important part of the course project, and prescribed templates could constrain the design space too much.

>>>>

We believe some annotations can be automatically detected;
for example, rather than requiring students to indicate if their kernel has a mechanism for disabling preemption apart from disabling interrupts, Landslide could detect when a timer interrupt is received but doesn't induce a context switch.
Other annotations, such as \x{tell_landslide_thread_runnable()}, could be replaced by mandating that the kernel's code paths in such cases include a function with a predetermined name.
Landslide already automatically instruments the memory allocator by detecting function names in the starter code; similar could be done for thread lifecycle and context switch events if their APIs were specified.
However, prescribing such templates has the downside of constrain the project's design space.
As open-ended decisions of interface design are important to the course philosophy, we foresee a tradeoff: in some cases, fundamental design challenges may be the cost for increasing Landslide's usability to enable teaching more advanced concepts such as SMP.

\shortversion{}{
Additionally, various improvements in Landslide's interface could increase its accessibility. 
For example, our class notes communicate execution sequencing with a tabular representation of thread execution; Landslide's presentation of a buggy sequence could be tailored to match our teaching methodology.
Landslide could also be extended with a mechanism for minimizing execution traces after a buggy one is found, to more accurately reflect which context switches are most relevant to the bug at hand.
}

@@

% Landslide needs to be extended to cope with the multiple scheduler queues that occur in multi-core hardware, however, much of this can be managed with slight variations of the annotations student provide, naming the core a thread will runs on, for example.

% To fully realize this benefit Landslide usability should be improved.

% this should all turn into a bulleted list of improvement areas
% Tool usability is greatly improved by lowering the start up effort required of each student.
% Much of the annotation our students must add to their kernel could be eliminated if the course project specification required prescribed names for prescribed functions, so Landslide could easily identify what the student kernel is doing.
% There is a downside to doing too much of this, as the design of kernel interfaces is an important part of the course project, and prescribed templates could constrain the design space too much.
